Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-11 Papers/ms.tex
Finished the bloody table!

The SIE+$\gamma$ has nine parameters:
the (circularized) einstein radius $b$, axis ratio $q$, central position
$(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
orientation angle of the external shear, $\theta_{\gamma}$.

@@

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
\hline
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=0, scale=0.1$\times$(image width))\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)T(-21, 21)\\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)T(-21, 21)\\
$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times$(image width), image width)\\
$W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times$(image width), image width)\\
$W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
\hline
{\bf Source Blob Parameters}\\
\hline
$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
$w_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
\hline
{\bf Lens Blob Parameters}\\
\hline
$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & Circular(location=$(x_c^{\rm lens}, y_c^{\rm lens})$, scale=$R_{\rm lens}$) \\
$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
\hline
{\bf Smooth Lens Parameters}\\
\hline
$b$ & SIE Einstein Radius & \\
$q$ & Axis ratio\\
$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position\\
$\theta$ & Orientation angle\\
$\gamma$ & External shear\\
$\theta_\gamma$ & External shear angle\\
\hline
{\bf Noise Parameters}\\
\hline
$\sigma_0$ & Constant component of noise variance\\
$\sigma_1$ & \\
\hline
{\bf Data}\\
\hline
$D_{ij}$ & Pixel intensities & Normal()
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}

>>>>

The SIE+$\gamma$ has nine free parameters:
the (circularized) einstein radius $b$, axis ratio $q$, central position
$(x_c, y_c)$, orientation angle $\theta$, the external shear $\gamma$, and the
orientation angle of the external shear, $\theta_{\gamma}$.

@@

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
\hline
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$(x_c^{\rm src}, y_c^{\rm src})$ & Typical position of source blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
$(x_c^{\rm lens}, y_c^{\rm lens})$ & Typical position of lens blobs & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
$R_{\rm src}$   &	Typical distance of source blobs from $(x_c^{\rm src}, y_c^{\rm src})$ & LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
$R_{\rm lens}$  &	Typical distance of lens blobs from $(x_c^{\rm lens}, y_c^{\rm lens})$ 	& LogUniform(0.01$\times$(image width), 10$\times$(image width))\\
$\mu_{\rm src}$ &	Typical flux of source blobs	& $\ln(\mu_{\rm src}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
$\mu_{\rm lens}$&	Typical mass of lens blobs	& $\ln(\mu_{\rm lens}) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
$W_{\rm max}^{\rm src}$ &		Maximum width of source blobs	& LogUniform(0.001$\times$(image width), image width)\\
$W_{\rm min}^{\rm src}$ &		Minimum width of source blobs	& Uniform(0, $W_{\rm max}^{\rm src}$)\\
$W_{\rm max}^{\rm lens}$ &		Maximum width of lens blobs	& LogUniform(0.001$\times$(image width), image width)\\
$W_{\rm min}^{\rm lens}$ &		Minimum width of lens blobs	& Uniform(0, $W_{\rm max}^{\rm lens}$)\\
\hline
{\bf Source Blob Parameters}\\
\hline
$(x_i^{\rm src}, y_i^{\rm src})$ & Blob position & Circular(location=$(x_c^{\rm src}, y_c^{\rm src})$, scale=$R_{\rm src}$)\\
$A_i$  & Blob flux & Exponential(mean=$\mu_{\rm src}$)\\
$w_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
\hline
{\bf Lens Blob Parameters}\\
\hline
$(x_i^{\rm lens}, y_i^{\rm lens})$ & Blob position & Circular(location=$(x_c^{\rm lens}, y_c^{\rm lens})$, scale=$R_{\rm lens}$) \\
$M_i$  & Blob mass & Exponential(mean=$\mu_{\rm lens}$)\\
$v_i$  & Blob width & Uniform($W_{\rm min}^{\rm src}$, $W_{\rm max}^{\rm src}$)\\
\hline
{\bf Smooth Lens Parameters}\\
\hline
$b$ & SIE Einstein Radius & LogUniform(0.001$\times$(image width), image width)\\
$q$ & Axis ratio & Uniform(0, 0.95)\\
$(x_c^{\rm SIE}, y_c^{\rm SIE})$ & Central position & iid Cauchy(location=$(0,0)$, scale=0.1$\times$(image width))\\
$\theta$ & Orientation angle & Uniform$(0, \pi)$\\
$\gamma$ & External shear & Cauchy$(0, 0.05)T(0, )$\\
$\theta_\gamma$ & External shear angle & Uniform$(0, \pi)$\\
\hline
{\bf Noise Parameters}\\
\hline
$\sigma_0$ & Constant component of noise variance & $\ln(\sigma_0) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
$\sigma_1$ & Proportionality coeff. for variance incr. with flux &
$\ln(\sigma_1) \sim$ Cauchy(0, 1)$T(-21.205, 21.205)$\\
\hline
{\bf Data}\\
\hline
$D_{ij}$ & Pixel intensities & Normal$(m_{ij}, s_{ij}^2 + \sigma_0^2 + \sigma_1m_{ij})$
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}
